Spit-Apply-Combine with Collapsing Groups

### 2022-11-02 paper/paper.tex
some ideas

\begin{itemize}
\item{Specification of collapsing sequence with multiple collapsing variables (e.g. first size class, then NACE code)}
\end{itemize}

>>>>

\begin{itemize}
\item{Specification of collapsing sequence with multiple collapsing variables (e.g. first size class, then NACE code). Idea: \texttt{collapse(data, by, formula, FUN,...)} where \texttt{formula} is
of the form \texttt{A0*B0 \~. A0*B1 + A1*B1 + A2*B1}. lhs is target level, rhs is collapsing sequence. }
\item{Specification of collapsing sequence with different aggregators per collapsing step.}
\item{Record-wise results}
\item{Record-wise imputation}
\item{Representation of hierarchical classifications: parent-child lists vs tabular}
\end{itemize}
